% xelatex
% vim:set noet sts=0 sw=8 ts=8 tw=80:
% \documentclass{article}
\documentclass{artikel1}
\usepackage[nobottomtitles*]{titlesec}

\author{SalahDin Ahmed Salh Rezk}
\title{The Lost Thought}

\begin{document}

\maketitle

\begin{abstract}
Here shall every writable thought of mine mere lost existence be. Considerable
thoughts are what is the most valuable to any capable intellect. It shall
neither be affected by what lies behind the collective nor the incapabilities of
the individual. Thus, this does not try to be anything other than what it really
is, to achieve — what I believe to be — the only noble goal to reach.
\end{abstract}

\section{The Collective}
\textit{Before individuality}

What I call ``The Collective" is the most effective yet the most harmful thing
to the individuality of a human condition. It may achieve the greatness that no
man can imagine, yet it actively chooses to not do a thing. Every day, the
collective does not care of what truly matters, yet it is in a constant
suffering for every failure it has experienced. Even if the failure was not of
its conscious at that particular of an instance; it would torture itself till
the point of absurdity.

The most risible to be seen of it is its ignorance. How confident it is just
amusing to any intellect of a mind to think with. It does not think of the facts
that of the mind. Instead, it works by the guide of a lost heart. It celebrates
the wrong, despises the right, and wonder what there is to be done in order to
whiten the blood that covers the floors of innocence. It is to be considered the
only clown of the entire circus of both unconscious and conscious existence of
the whole. 

The Collective, however, existed long before anything. It was the start and may
be the end. It was the continuation and may be the interruption. It was nothing
before but would never be everything to see. It helped everything to come and
helped everyone to fall. It never cared but always looked into what is beneath
to be cared.

What different yet similar instances of consciousness that unrealistically think
do not belong to The Collective, which I would believe to be the falsest of
thoughts for a long time in the current whole, oppose it. They do not comprehend
how much they are part of it and how much it is a part of them. There no thing
to be seen to exist separate to The Collective yet. They avoid the unlikable
notion of belonging to it and its ramifications. The meaning of being a part yet
oppose the whole is the most antithetical of ideas, which who believe to be
apart hate.

I would be arrogant to decide the state of The Collective. It may be — no matter
how much I believe it to be utterly stupid — the most magnificent capable
intellect of conscious and the opposite to be comprehensible in the plane of
thought and nonexistence.

\section{The Self}
\textit{Within The Collective}

To not be the self is to tolerate the unfulfilling need for its completion with
no act towards the desired existence to be. To not be the self is to wait for
the unwaited victory of the nonexistence in the plane just like the
incompletenesses of whatever lies inside one's condition. To not be the self is
to not realize the agony of existence and what is beneath. Many of whom not
think, despite that, fail to recognize this factious implication. They do waste
their existence to neither the whole nor what truly matters. Instead, they give
every consciousness of existence, every intellect of mind, every notion of
thought, and even every deed that could ever matter to what never mattered, to
what never delivered, and to what never even promised to be. They lose the being
of the end; the only being to be avoided in the cost of the one's act. The most
absurd of all actions that of a human to be done.

In contrast, to be the self is one of the noble goals to reach. It is to be the
truth with no regard to The Collective. It is to exist within both the planes of
existence and the thought with regard to the most of what truly matter. However,
the pursuit of the self is undesired for the lost hearts of whom to be without.
One's shall be the one to exist between who belong to The Collective, to be the
one to recognize and praise whilst still being the individual. Being in harmony
whilst ignoring the pitfalls of The Collective may be considered the narrowest
of paths to follow; The Collective would consume the conscious until the time of
the end, but if the opposite is achieved, it is one's finest of states to be in
within the whole.

Break whatever shall be in the way of the noble, help everyone to be, and exist
for seeking whatever to be seen behind the walls of realization are what truly
makes ``The Path". Intellects, however, desire the paths of whomever lost the
nobility within their heart and the mind within their being, the open path of
the end to be taken from one's existence beyond the cosmos.

\section{Beyond Realization}
\textit{The notion of thought and itself}

The realization of whatever lies inside of the unconscious of the whole and
before is arguably the hardest of all things to do. Many of whom search the
truth and the mind of existence do think that they reached the realization.
However, they are too blind to see how broken the glass of the cosmic. They are
blinded by both the ignorance of the state and the arrogance caused by The
Collective. It may be considered impossible to count the number of conscious
beings believing to realize, yet the worst is who believe they went beyond it.

There shall be no existence that fully grasp what that is beyond there within
this limited spaces of thought and existence of self. It is always wearisome to
mine seeing whoever thinks be too invested with the pursuit of realization that
they forget what truly matters. Minds do not prefer realization due to the fears
it holds, the promises it makes, and the laws it breaks. It does not promise the
most achievable of roads, the happiest of moments, nor the fulfilment of what
lies inside the self and beyond. It promises what really is with no care to
whatever may any comprehension believe to be cared about. That is — what I
believe to be — the only noble act to be in the whole.

The fact is, in addition, there shall always be realizations above what a
conscious truly grasps in order for the thought of to be held true, which is the
case no matter what who do not think believe. There might be some minds that do
realize this fact in the infinite realm of possibilities, which are to be
considered beyond one's comprehension.

\section{A Value}
\textit{What was given}

What can be seen through the vast lands of what is underneath is the values that
are given by the intellects of who do exist to whatever lies on the black
carpets of meaningless deed. That is to be the most likable thing for The
Collective, which inevitably forces the individual of a human condition to lose
his existence to the values that should not be cared about. Every structure of
intention shall be with with no regard to whatever values might be given to them
by whomever think.

Values of the subjective instances of existence shall not be favored with the
objective nonexistent thoughts in hand of free minds of the whole, yet The
Collective praises this the most. It builds everything on the dishonourable
values given to what to be thought of, all that to be in the human nature. This
is unbelievably wrong to what lies before the conscious of mind itself. This may
expedite the progress in the current, but it is bound to lead the downfall of
human intellect. Countless edifications fell onto the ground of what to be
erroneous only because that of wrong value.

It is most unfortunate that the values of whichever is are the motivation to be
for many. The mistake of them existing and depending on them was not enough for
some; they had to make their life and its meaning itself tied to what shall not
be. The fools who does this are destined to their painful shallow of meaning
death. Whom shall not ascend to the righteousness that of beyond the existence
are alike, cannot smell what is really disgusting of everything and think they
are the remnants.

\section{A Conflict}
\textit{One among many}

Thinking and acting with whom are not the self is an invaluable part of the
experience of mind's conscious intellect, yet many take the opportunity to do
what is hated by all to be. They do not realize that only who not think does
alike. Thinkers believe that conflicts are the modus operandi to ascend into
what is true; the only way to approach what exists beyond. Despite that, they
struggle until crumbling into what not to be seen by any.

The disunity of who do not think is the catastrophe for what exists underneath.
What to be done is the most disgraceful of all. They spread their inferiority to
all corners of the lands to live in; no one can escape the agony to be
experienced caused by that of the done acts. And for what? For the planes? For
the doctrines? For what shall be? The mislay of one's self beyond the void is
their kismet. Shall they learn of what the past brought to their eyes, yet they
are blind.

Natheless, what to effectuate as a mere lost soul? The acts of ginormous
conflict are not that of normals. They are that of princes; to whom power is
given doing whatever comes to one's mind. Princes are used to kill and care not,
to starve out and feel not, and to live and die not. They are, however, not more
than a bare reflection to the true nature of the mortals under. It may seem to
the illiterate that princes are the ones to blame — which I believe to not be
completely false. However, a one of true compos mentis will realize the true
soreness that exists among many. The blame shall lay on neither the princes of
potency nor the personage of fallibility but on the root of all causes of
vendetta, what verily lies inside the human condition.

We, the mortals of quotidian, are the ones holding the Excalibur of every deed
that may ever affect any whom. The only hindrance to be seen lies inside our own
self. Thence, the radical change to be done is to ourselves, not to the world
that have punished us for what we did not have the serendipity to do. It is,
nonetheless, a difficult act to achieve; one should not only change what lies
inside their very own selves, but also the innermost of all people among, parts
of The Collective which are arduous to change. The thinker of thinkers should,
despite that, always try to accomplish the impossible of tasks to advance — not
only himself but also The Collective — over the current. Shall the mortals gain
wisdom from who earnestly thinks for transmogrification.

\section{Modicum of The Parts}
\textit{Fractions of the whole}

The fractious nature of even ``The Parts" themself is an essential notion to
realize in order to advance over the current. Whatever shall be is a modicum of
a commodity. Every division is a fraction itself, this is the rationale all the
way down to the axioms of the whole. Nothing shall be exception to this pristine
aphorism. It is, however, the contradiction to be made with the human condition;
they can not yet grasp the true potential of such a beyondless soupçon.

For the wish of progress over the current, this principa is indispensable. Those
who are sagacious would realize the true potential due to their quiddity being
over what is seen by the senseless. Despite that, it did not lay in many
thinkers' power. Instead, they lost every worthwhile instance of themselves to
the end. One shall be the thinker of thinkers; whom are guided by do no fall to
the woe, but they endeavour the hated in lieu.

\section{Derogation From Freedom}
\textit{How shall one's leisure be}

The freedom of one's self is the best idea a man have ever came up with yet will
be for the longest one of the most detrimental. Most of who exist do not think
of every action they do at every moment they live. Instead, they let the events
surrounding their existence move them in whatever direction shall be. The result
of such a careless philosophy is the misuse of whatever they are free to do:
kill who live, do what not to be done, and use the harmful to one's.

Howbeit, the less free we can think the worse the decisions to be made in the
world of existence, and what to be seen is not the desired one. It has been the
way for the longest chapter of the history of humanity and whomever is beside,
so we assiduously know that freedom of whatever is could often be the solution
to the suffering that may be. The way, therefore, is to use the finest balance
between what is possible and what could be done by a thinking intellect of minds
and whichever be.

\end{document}
